Survey on Aspect-Based Sentiment Analysis

### 2023-04-28 paper/paper.tex
another one

\begin{abstract}
This document is a model and instructions for \LaTeX.
This and the IEEEtran.cls file define the components of your paper [title, text, heads, etc.]. *CRITICAL: Do Not Use Symbols, Special Characters, Footnotes, 
or Math in Paper Title or Abstract.
\end{abstract}

\begin{IEEEkeywords}
component, formatting, style, styling, insert
\end{IEEEkeywords}

@@

(Add specific examples of techniques being used in the past and present for ABSA here later)

@@

The paper correctly concluded a better performance than LDA-based models. However, there was not substantial improvement over the other mainstream models being used such as the $k$-means and the biterm topic model (BTM).

@@

@@

\subsection{Before 2011}

@@

\subsection{Equations}
Number equations consecutively. To make your 
equations more compact, you may use the solidus (~/~), the exp function, or 
appropriate exponents. Italicize Roman symbols for quantities and variables, 
but not Greek symbols. Use a long dash rather than a hyphen for a minus 
sign. Punctuate equations with commas or periods when they are part of a 
sentence, as in:
\begin{equation}
a+b=\gamma\label{eq}
\end{equation}

Be sure that the 
symbols in your equation have been defined before or immediately following 
the equation. Use ``\eqref{eq}'', not ``Eq.~\eqref{eq}'' or ``equation \eqref{eq}'', except at 
the beginning of a sentence: ``Equation \eqref{eq} is . . .''

\subsection{Figures and Tables}
\paragraph{Positioning Figures and Tables} Place figures and tables at the top and 
bottom of columns. Avoid placing them in the middle of columns. Large 
figures and tables may span across both columns. Figure captions should be 
below the figures; table heads should appear above the tables. Insert 
figures and tables after they are cited in the text. Use the abbreviation 
``Fig.~\ref{fig}'', even at the beginning of a sentence.

\begin{table}[htbp]
\caption{Table Type Styles}
\begin{center}
\begin{tabular}{|c|c|c|c|}
\hline
\textbf{Table}&\multicolumn{3}{|c|}{\textbf{Table Column Head}} \\
\cline{2-4} 
\textbf{Head} & \textbf{\textit{Table column subhead}}& \textbf{\textit{Subhead}}& \textbf{\textit{Subhead}} \\
\hline
copy& More table copy$^{\mathrm{a}}$& &  \\
\hline
\multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
\end{tabular}
\label{tab1}
\end{center}
\end{table}

\begin{figure}[htbp]
\centerline{Picture here}
\caption{Example of a figure caption.}
\label{fig}
\end{figure}

Figure Labels: Use 8 point Times New Roman for Figure labels. Use words 
rather than symbols or abbreviations when writing Figure axis labels to 
avoid confusing the reader. As an example, write the quantity 
``Magnetization'', or ``Magnetization, M'', not just ``M''. If including 
units in the label, present them within parentheses. Do not label axes only 
with units. In the example, write ``Magnetization (A/m)'' or ``Magnetization 
\{A[m(1)]\}'', not just ``A/m''. Do not label axes with a ratio of 
quantities and units. For example, write ``Temperature (K)'', not 
``Temperature/K''.

>>>>

\begin{abstract}
Aspect-based Sentiment Analysis (ABSA) is a very important field within Natural Language Processing (NLP). It has 2 major tasks which are Aspect Extraction (AE) and Aspect Sentiment Classification (ASC). With the increasing amount of reviews, blogs, articles, and other opinion-based texts which are produced for every possible entity such as places (restaurants, schools), food items, and products; there is no surprise that the stakeholders of these entities value the critical feedback and hope for efficient ways to analyze this large amount of feedback and opinions. From statistical models in the beginning to the neural models of today. From RNN based models to BERT based models. This field has experienced a wide array of techniques. These days we can see the attempt to move from Supervised and Semi-Supervised approaches to Unsupervised ones so that finally the promise of ABSA is realized; to extract aspect specific sentiments without being constrained by labeling and domain. In this paper, the many approaches that have been used over the years to perform ABSA will be explored so that we can derive an understanding and appreciation of how far we have come in our progress in this field.
\end{abstract}

@@

@@

The paper correctly concluded a better performance than LDA-based models. However, there was not substantial improvement over the other mainstream models being used such as the $k$-means and the biterm topic model (BTM).\\

@@

The most common approach for SA and ABSA at the time of this paper was LDA as mentioned in the previous review. This paper proposes to extend the LDA approach by adding an additional sentiment layer. The new model is referred to as the weakly supervised joint sentiment-topic (JST) model.

JST was distinguished from the other ABSA models at the time in that it is weakly supervised, so the only supervision comes from a domain independent sentiment lexicon, and that it can detect aspects and sentiments simultaneously. The authors believed that it's weakly supervised nature would make it portable to other domains of SA. The idea behind JST was that aspects are generated based on the sentiment distributions and the words are generated based on the sentiment-aspect pairs.

The existing LDA model is based on the assumption that a document is a mixture of aspects and each aspect is a probability distribution over words. The LDA model goes through the document and calculates the probability for each word to belong to a certain topic given the document (from a predetermined list of topics). Figure 9 gives a graphical representation of the JST model.

\begin{figure}[htbp]
\centerline{\includegraphics[keepaspectratio, width=0.5\textwidth]{pics/9.png}}
\caption{A graphical representation of the JST model made by C. Lin et al. in their study.}
\label{fig}
\end{figure}

It starts with $S$, the distinct sentiment labels, $T$, the topics, and $D$, a collection of documents. Each document is a list of words from a vocabulary $V$. First, we make a distribution of words for each sentiment-topic pair using the vocabulary. For each document we select a distribution of sentiment labels, then for each label under that document we select a distribution sentiment-topic pairs. Then for each word we select a sentiment label, then a topic, then finally a word from a distribution of words that are related to that topic and sentiment label. Thus, for a given document, its contained topics (aspects) and their sentiments are derived.

This model is an extension and improvement over the baseline LDA model. And as per the results quoted, it does show a significant improvement over the baseline LDA model on the same datasets. The authors also experimented with a reverse-JST model which selected a topic and then a sentiment instead of the other way around. reverse-JST showcased similar results to the JST model.\\

@@

\subsection{2011 and Before}

\textit{\textbf{Multi-aspect Sentiment Analysis with Topic Models, B. Lu et al., 2011.}}

hey

halo\\

@@

\textit{\textbf{Sentiment Analyzer: Extracting Sentiments about a Given Topic using Natural Language Processing Techniques, J. Yi et al., 2003.}}

This paper introduces a very early approach to perform ABSA. It correctly identifies the needs and the motivation to perform ABSA, which with time have only grown. This can be seen by the fact that in the 20 years after the publication of this paper, the statements regarding the need for ABSA have only become truer.

This paper introduces a statistical model that takes in a document and extracts from the document topic-specific features. It then extracts all the opinion bearing phrases from the document and deduces their sentiment. Finally it makes the (topic$\mid$feature, sentiment) relations. For example, for the domain of digital camera, a feature is a part of the camera such as the lenses, a feature of the camera such as the price, or a feature of a part of the camera such as the battery life.

The paper identifies that the feature terms are usually nouns and then focuses on these for the feature term extraction algorithm. They tested 3 heuristics for candidate term selection: Base Noun Phrases (BNP),  Definite Base Noun Phrases (dBNP), and Beginning Definite Base Noun Phrases (bBNP). The paper develops 2 algorithms to perform feature extraction, one based on a mixture language model and the other based on likelihood ratio.

In the first algorithm, the authors note that a document can be considered to be generated by a linear combination of the general web language model $\theta_W$ (similar to the corpus language model), and the  topic-specific language model $\theta_T$ (similar to the query model):
\begin{equation*}
  \theta = \alpha \theta_W + \beta \theta_T
\end{equation*}
where $\theta$, $\theta_W$, and $\theta_T$ are multidimensional distributions over the number of words in the corpus. The idea is to calculate the $\theta_{T_i}$ score for each term in a document. Then the feature terms with their score satisfying some confidence level are selected. For the likelihood test algorithm, we compute the likelihood score for each candidate feature term, and then select the terms which satisfy some confidence level.

\begin{figure}[htbp]
\centerline{\includegraphics[keepaspectratio, width=0.5\textwidth]{pics/14.png}}
\caption{A comparison of the precision of the different feature term extraction algorithms over the digital camera and the music corpora.}
\label{fig}
\end{figure}

As can be seen from Figure 10, the bBNP heuristic with the likelihood score algorithm yielded the best accuracy for feature term extraction.

The actual sentiment analysis part of the feature terms is done by using a sentiment pattern database which matches patterns in the text to defined sentiment patterns and assigns the matches sentiments accordingly. It is easy to see that this statistical approach is a rather primitive compared to the powerful neural models of today and that it will suffer from very high domain adaptability issues and that it might suffer from input such as customer reviews which use informal expression and language which will will make it difficult to capture all sentiment patterns that can occur.

That being said it still performs relatively well on general web documents and news articles as indicated by the results obtained. This points to the ingenuity of this idea of performing ABSA with very limited resources for the time using a statistical model.

\section{Conclusion}
